Structural controllability of ecological networks

### 2018-06-26 paper/manuscript.Rmd
comments and edits to captions of figs 5 and 6

<!-- DBS: I don't understand the description of (b) below about the values predicted by the most parsimonious model. I think it needs more info to be fully intelligible. -->
```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="Drivers of network controllability. (a) Probability density of the relative size of the minimum driver-node set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks. (b) The relationship between the asymmetry plant/pollinator richness and $n_D$. The plot shows the values predicted by the most parsimonious model. (c) Probability density of the difference between the relative size of the minimum driver-node set of random networks and that of empirical networks. We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line). The vertical dashed lines in (a) and (c) indicate the median values of the distributions."}
drake::loadd(fig_emp_controllability)
fig_emp_controllability %>%
  purrr::map(function(x) x + theme(plot.margin = grid::unit(c(0.5, 1.5, 0.5, 1.5), "mm"))) %>% {
    cowplot::plot_grid(plotlist = ., 
                     nrow = 1, 
                     align = "h")
  }

@@

```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot of the control capacity $\\phi$ of (a) plants and (b) pollinators. The control capacity of all invasive species is $\\phi = 1$ and is depicted with solid circles."}
drake::loadd(fig_control_capacity)
fig_control_capacity[[2]] <- fig_control_capacity[[2]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())

# pdf("test.pdf", width =fig_sizes()[[2]]*2/3, height = fig_sizes()[[1]])
fig_control_capacity %>%
    cowplot::plot_grid(plotlist = ., rel_widths = c(1.21,1), align = "h")
# dev.off()
```

```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Model averaged partial residual plots for the relationship between control capacity and (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree."}
drake::loadd(fig_species_partial)
fig_species_partial %>%
  purrr::map_at(2:4, function(x) x  + theme(axis.title.y = element_blank(), axis.text.y = element_blank())) %>%
    cowplot::plot_grid(plotlist = ., align = "h", nrow = 1, rel_widths = c(1.25, 1, 1,1))
```

@@

```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Density plot of the structural stability of the communities after a focal species is removed. The structural stability after critical species have been removed (darker line) is considerable smaller than the average. To allow comparison across communities, the structural stability values were scaled within each network to have a mean of 0 and a standard deviation of one."}
drake::loadd(fig_structural_stability)
fig_structural_stability[[1]]
```

>>>>

<!-- DBS: I don't understand the description of (b) below about the values predicted by the most parsimonious model. I think it needs more info to be fully intelligible. -->
<!-- DBS: y-axes in (a) and (c) should be "probability density" -->
```{r fig-emp-controllability, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap="Drivers of network controllability. (a) Probability density of the relative size of the minimum driver-node set $n_D$ in the invaded (light) and uninvaded (dark) empirical networks. (b) The relationship between the asymmetry plant/pollinator richness and $n_D$. The plot shows the values predicted by the most parsimonious model. (c) Probability density of the difference between the relative size of the minimum driver-node set of random networks and that of empirical networks. We randomised either the species visitation patterns (light line) or randomised the direction of control between a species pair (dark line). The vertical dashed lines in (a) and (c) indicate the median values of the distributions."}
drake::loadd(fig_emp_controllability)
fig_emp_controllability %>%
  purrr::map(function(x) x + theme(plot.margin = grid::unit(c(0.5, 1.5, 0.5, 1.5), "mm"))) %>% {
    cowplot::plot_grid(plotlist = ., 
                     nrow = 1, 
                     align = "h")
  }

@@

<!-- DBS: y-axis in (a) should be "probability density" -->
<!-- DBS: I also *love* this plot. -->
```{r fig-species-level, fig.width=fig_sizes()[[2]]*2/3, fig.height=fig_sizes()[[1]]/2, fig.cap="Probability density of the control capacity $\\phi$ of (a) plants and (b) pollinators across all networks. The control capacity of all invasive species is $\\phi = 1$ and is depicted with solid circles."}
drake::loadd(fig_control_capacity)
fig_control_capacity[[2]] <- fig_control_capacity[[2]] +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())

# pdf("test.pdf", width =fig_sizes()[[2]]*2/3, height = fig_sizes()[[1]])
fig_control_capacity %>%
    cowplot::plot_grid(plotlist = ., rel_widths = c(1.21,1), align = "h")
# dev.off()
```
<!-- DBS: You never state in the methods what you mean by model-average partial residuals. If you don't explain it there, you MUST explain it here as there is a good chance that no one will invest the time required to know what is actually going on. -->
```{r fig-species-partial, fig.width=fig_sizes()[[2]], fig.height=fig_sizes()[[1]]/2, fig.cap= "Model-averaged partial-residual plots for the relationship between control capacity and (a) contribution to nestedness, (b) visitation strength, (c) asymmetry of dependences, and (d) degree."}
drake::loadd(fig_species_partial)
fig_species_partial %>%
  purrr::map_at(2:4, function(x) x  + theme(axis.title.y = element_blank(), axis.text.y = element_blank())) %>%
    cowplot::plot_grid(plotlist = ., align = "h", nrow = 1, rel_widths = c(1.25, 1, 1,1))
```

@@

<!-- DBS: y-axis should be "probability density" -->
<!-- DBS: remove the title at the top of the figure -->
<!-- DBS: the issue of scaling of Omega should likely appear in the methods too... -->
```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Probability density of the structural stability of the communities after a single focal species is removed. The structural stability after critical species have been removed (darker line) is considerable smaller than that after non-critical (redundant) species have been removed. To allow comparison across communities, the structural stability values were scaled within each network to have a mean of zero and a standard deviation of one."}
drake::loadd(fig_structural_stability)
fig_structural_stability[[1]]
```
